Plots for Latent Hawkes Paper

### 2020-12-10 output_scripts/Paper_Plots.Rmd
some final updates for plots

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "paper_figure/",
                      dev = 'pdf', fig.height = 4.5, fig.width = 7,
                      warning = FALSE)

@@

current_cohort <- 5

@@

  if(testing_end>ncol(temp_gl$history[,,1])){
    history_matrix <- cbind(history_matrix,
                            t(matrix(rep(history_matrix[,ncol(history_matrix)],
                                         testing_end-ncol(temp_gl$history[,,1])),
                                     nrow=testing_end-ncol(temp_gl$history[,,1]),
                                     byrow=TRUE)))
  }else{
    # this line makes no sense, and should likely never happen
    # try(
    history_matrix <- history_matrix[,1:testing_end]#temp_gl$history[,1:testing_end]
    # )
  }
  sim_gl_array[,,s] <- history_matrix[,training_end:testing_end]
}
```

```{r fig-10a-glicko-rating}
par(mar=c(3,5,3,1))
plot(1, type="n", xlab="", ylab="Glicko ranking", xlim=c(0,dim(gl$history)[2]),
     ylim=c(min(gl$history[,,1]),max(gl$history[,,1])),
     cex.axis=2, cex.lab=2)
for(m in c(1:mice_number)){
  #history
  lines(gl$history[m,1:training_end,1],
        cex=0.6, col=col_vec[m],lwd=history_width,lty=ltypes_vec[m])
  lines(c(rep(NA,training_end), gl$history[m,(training_end+1):testing_end,1]),
        cex=0.6, col=shade_vec[m],lwd=history_width,lty=ltypes_vec[m])

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "paper_figure/",
                      dev = 'png', fig.height = 4.5, fig.width = 7,
                      warning = FALSE)

@@

current_cohort <- 7
# 4 best so far, or 7

@@

  if(testing_end>ncol(temp_gl$history[,,1])){
    history_matrix <- cbind(history_matrix,
                            t(matrix(rep(history_matrix[,ncol(history_matrix)],
                                         testing_end-ncol(temp_gl$history[,,1])),
                                     nrow=testing_end-ncol(temp_gl$history[,,1]),
                                     byrow=TRUE)))
  }else{
    # try(
    history_matrix <- history_matrix[,1:testing_end]#temp_gl$history[,1:testing_end]
    # )
  }
  sim_gl_array[,,s] <- history_matrix[,training_end:testing_end]
}
```

```{r fig-10a-glicko-rating}
par(mar=c(3,5,3,1))
testing_end <- testing_end - 1
plot(1, type="n", xlab="", ylab="Glicko ranking", xlim=c(0,dim(gl$history)[2]),
     ylim=c(min(gl$history[,,1]),max(gl$history[,,1])),
     cex.axis=2, cex.lab=2)
for(m in c(1:mice_number)){
  #history
  lines(gl$history[m,1:training_end,1],
        cex=0.6, col=col_vec[m],lwd=history_width,lty=ltypes_vec[m])
  lines(c(rep(NA,training_end), gl$history[m,(training_end+1):testing_end,1]),
        cex=0.6, col=shade_vec[m],lwd=history_width,lty=ltypes_vec[m])
